### 2019-03-04 report/final-report.tex
section 5

In this project, we designed, analyzed and implemented algorithms that
synthesize three classes of bidirectional transformations: (1) pure
bijective transformations, (2) bijections modulo equivalences classes
(quotient lenses) and (3) bijections modulo projections (simple symmetric
lenses).  Our synthesis algorithms take as inputs a format specification
(which includes specification of equivalence classes) and a collection of
examples.  As the class of transformations becomes richer, the number of
potential programs grows dramatically.  As a result, the corresponding
inference algorithm slows and its ability to guess the transformation
desired by the user decreases, leading to reduced accuracy.  We overcame
these challenges through new heuristics that use information theory to help
guide the search for program transformations.  In addition, to scale our
prototype to larger transformation tasks, we found it necessary to work
compositionally, by breaking down complex synthesis tasks into smaller, more
mangeable subtasks.

@@

\section{List of Symbols, Abbreviations, and Acronyms}
\begin{longtable}{p{1in}p{5in}}
  \ToDNFRegex{}         & An operation that converts regular   expressions into DNF form\\
  \ToLens{}             & An operation that converts a DNF lens to a  lens \\
  $\equiv_S$, $\equiv_T$ & Equivalence relations on data matching
                           regular expressions $S$ and $T$
                           respectively \\
  \AnyOpt{}             & Mode for simple symmetric synthesis that ignores the information-theoretic metric \\ 
  AST     & Abstract syntax tree\\  
  \BSOpt{}              & Bijective lens synthesis algorithm\\
  DARPA   & Defense Advanced Research Project Agency \\
  \CCOpt{}              & Mode for simple symmetric synthesis that
                          replace our information-theoretic cost metric with one where 
                          the cost of the lens is the number of disconnects plus the number
                          of merges.\\
  \DNFLens{}            & Lens in disjunctive normal form\\
  DNF                   & Disjunctive normal form\\
  \DNFRegex{}, \DNFRegexAlt{}  & Regular expression in disjunctive normal form\\
  \Examples{}           & Examples \\
  \Expand       & A component of the synthesis algorithm that proposes candidate
                  types equivalent to the input \\
  \FLOpt{}              & Mode for simple symmetric synthesis that
                          returns the first highest ranked lens found
                          by  \GreedySynth \\
  \footnotesize{\GreedySynth} & Synthesis procedure that searches greedily for candidate
                 solutions \\
  HR & Human Resources \\
  HTML & Hyptertext Markup Language \\
  JSON & JavaScript Object Notation---a standard file format used to
         encode data objects\\
  \Lens{}               & A lens \\
  $\mathcal{L}(\BRegex{})$  & The language of strings for the regular expression
                             \BRegex{} \\
  \NROpt{}              & Mode for simple symmetric synthesis that
                          ignores all \SRequire annotations in the SRE specifications. \\
  \NSOpt{}              & Mode for simple symmetric syntehsis that
                          ignores all \Skip annotations in the SRE specifications. \\ 
  \Optician{} & Our prototype implementation of the lens synthesis algorithms \\
  QRE                   & Quotient regular expression\\
  \textbf{QS}  & Number of nodes in the abstract syntax of QRE specifications \\
  RDF & Resource Description Framework---used to model web resources \\
  REST & Representational State Transfer\\
  SRE                   & Stochastic regular expression\\
  \BRegex and \BRegexAlt & Regular expressions provided by the user\\
  \Regex{}, \RegexAlt{} & Regular expressions\\
  $S \Leftrightarrow T$ & Type of a lens that maps between data
                          described by regular expressions $S$ and $T$\\
  \SSOpt{}              & Full symmetric synthesis algorithm\\
  \SSNCOpt{}            & Symmetric synthesis algorithm without using a library of
    existing lenses.\\
  {\footnotesize \SynthDNFLens{}} & A type-directed lens synthesis algorithm \\
  XML & Extensible Markup Language---used in web services \\
\end{longtable}

>>>>

In this project, we designed, analyzed and implemented algorithms that
synthesize three classes of bidirectional transformations: (1) pure
bijective transformations, (2) bijections modulo equivalences classes
(quotient lenses) and (3) bijections modulo projections (simple symmetric
lenses).  Our synthesis algorithms take as inputs a format specification
(which includes specification of equivalence classes) and a collection of
examples.  As the class of transformations becomes richer, the number of
potential programs grows dramatically.  As a result, the na\"{i}ve
inference algorithm slows and its ability to guess the transformation
desired by the user decreases, leading to reduced accuracy.  We overcame
these challenges by applying heuristics that use information theory to help
guide the search for program transformations.  In addition, to scale our
prototypes to larger transformation tasks, we found it necessary to work
compositionally, by breaking down complex synthesis tasks into smaller, more
mangeable subtasks.  The resulting system, embodied by (variants of) our
prototype \Optician{} implementation, out perform existing state-of-the-art
tools for synthesis tasks in this domain.

@@

\section{List of Symbols, Abbreviations, and Acronyms}
\begin{longtable}{p{1in}p{5in}}
  \ToDNFRegex{}         & An operation that converts regular   expressions into DNF form\\
  \ToLens{}             & An operation that converts a DNF lens to a  lens \\
  $\equiv_S$, $\equiv_T$ & Equivalence relations on data matching
                           regular expressions $S$ and $T$
                           respectively \\
  \AnyOpt{}             & Mode for simple symmetric synthesis that ignores the information-theoretic metric \\ 
  AST     & Abstract syntax tree\\  
  \BSOpt{}              & Bijective lens synthesis algorithm\\
  DARPA   & Defense Advanced Research Project Agency \\
  \CCOpt{}              & Mode for simple symmetric synthesis that
                          replace our information-theoretic cost metric with one where 
                          the cost of the lens is the number of disconnects plus the number
                          of merges.\\
  \DNFLens{}            & Lens in disjunctive normal form\\
  DNF                   & Disjunctive normal form\\
  \DNFRegex{}, \DNFRegexAlt{}  & Regular expression in disjunctive normal form\\
  \Examples{}           & Examples \\
  \Expand       & A component of the synthesis algorithm that proposes candidate
                  types equivalent to the input \\
  \FLOpt{}              & Mode for simple symmetric synthesis that
                          returns the first highest ranked lens found
                          by  \GreedySynth \\
  \footnotesize{\GreedySynth} & Synthesis procedure that searches greedily for candidate
                 solutions \\
  HR & Human Resources \\
  HTML & Hyptertext Markup Language \\
  JSON & JavaScript Object Notation---a standard file format used to
         encode data objects\\
  \Lens{}               & A lens \\
  $\mathcal{L}(\BRegex{})$  & The language of strings for the regular expression
                             \BRegex{} \\
  \NROpt{}              & Mode for simple symmetric synthesis that
                          ignores all \SRequire annotations in the SRE specifications. \\
  \NSOpt{}              & Mode for simple symmetric syntehsis that
                          ignores all \Skip annotations in the SRE specifications. \\ 
  \Optician{} & Our prototype implementation of the lens synthesis algorithms \\
  \Optician{}$_Q$ & Optician enhanced with support for QRE synthesis \\
  QRE                   & Quotient regular expression\\
  \textbf{QS}  & Number of nodes in the abstract syntax of QRE specifications \\
  RDF & Resource Description Framework---used to model web resources \\
  REST & Representational State Transfer\\
  SRE                   & Stochastic regular expression\\
  \BRegex and \BRegexAlt & Regular expressions provided by the user\\
  \Regex{}, \RegexAlt{} & Regular expressions\\
  $S \Leftrightarrow T$ & Type of a lens that maps between data
                          described by regular expressions $S$ and $T$\\
  \SSOpt{}              & Full symmetric synthesis algorithm\\
  \SSNCOpt{}            & Symmetric synthesis algorithm without using a library of
    existing lenses.\\
  {\footnotesize \SynthDNFLens{}} & A type-directed lens synthesis algorithm \\
  XML & Extensible Markup Language---used in web services \\
\end{longtable}
